

Before all others, I thank my extended mathematical family for making me believe in the
family metaphor.
Tom, Chan, Mehmet, and Li-Mei created such a fun and friendly atmosphere that I couldn't
help but fall in, immediately at home.
Thank you to my advisor Jeff, whose advice and worldview has had profound positive effects
on my experience as a graduate student.


Much of the work in this thesis was either directly or indirectly inspired by
collaboration with my mathematical family.
Chapter~\ref{c:sums} was born out of a question asked by Jeff Hoffstein at his 61st
birthday conference concerning the sign changes of sums of coefficients of cuspforms,
which I thought about immediately afterwards with Tom Hulse, Chan Ieong Kuan, and Alex
Walker.
This eventually led to both the ideas of Chapter~\ref{c:sums} and the papers briefly
described in Chapter~\ref{c:sums_apps}.
The main question of Chapter~\ref{c:hyperboloid} was brought to my attention by Chan Ieong
Kuan and Mehmet K{\i}ral several years ago.
During our first (somewhat misguided) attempts, I learned a lot about mathematics and
collaboration, and I owe them much.


Thank you to Paul and Miles, for the countless hours both in and outside of work together,
and for talking endlessly about the Mean Value Theorem with me.
I would also like to thank all my other collaborators, for helping make math fun.


Thank you to Jill, Joe, Mike, Reinier, and Dinakar for serving on my committees.


Thank you in particular to my little brother Alex for the companionship and collaboration,
and to my soon-to-be little sister-in-law-in-math Sara for tolerating our many months
living together.


Finally, I want to thank Joanna, my parents, and my family for their love and support.
They don't always understand what I think about, but they care anyway.


I love you all.

\noindent
\begin{tabular*}{\textwidth}{c}
  \midrule
\end{tabular*}
This material is based upon work supported by the National Science Foundation Graduate
Research Fellowship Program under Grant No. DGE 0228243.


